### 2022-09-14 paper/Chapters/Chapter05.tex
update paper

%% mean metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 35.66 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
		\hline
		BS 			& 31.93 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
		\hline
		DG 			& 39.57 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
		\hline
		GF 		& 39.69 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
		\hline
		WS 		& 42.83 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
		\bottomrule
	\end{tabular}
	\caption{Average angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 34.06 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
		\hline
		BS 			& 34.14 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
		\hline
		DG 			& 36.43 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
		\hline
		GF 		& 37.60 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
		\hline
		WS 		& 36.89 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
		\bottomrule
	\end{tabular}
	\caption{Median angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l |l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 0.59\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
		\hline
		BS 			& 0.36\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
		\hline
		DG 			& 0.32\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
		\hline
		GF 		& 0.38\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
		\hline
		WS 		& 0.18\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 3.48\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
		\hline
		BS 			& 5.19\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
		\hline
		DG 			& 2.25\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
		\hline
		GF 		& 2.50\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
		\hline
		WS 		& 1.95\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 18.18\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
		\hline
		BS 			& 26.26\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
		\hline
		DG 			& 13.58\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
		\hline
		GF 		& 13.02\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
		\hline
		WS 		& 14.29\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 37.22\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
		\hline
		BS 			& 43.03\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
		\hline
		DG 			& 29.87\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
		\hline
		GF 		& 27.03\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
		\hline
		WS 		& 27.67\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-30d}
\end{table}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison of GCNN based models. (Resolution: $ 128\times 128 $)}
	\label{fig:gcnn-eval-multi-model}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f3.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
	\label{fig:tripnet-fusion-eval}
\end{figure}

>>>>

%% mean metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 22.58 & 11.08 & 13.13 & 13.71 & 10.14 & 10.66 & 10.66 & \textbf{10.09} \\ 
		\hline
		BS 			& 19.78 & 7.17 & 8.67 & 11.71 & \textbf{6.85} & 7.52 & 7.93 & 7.09 \\ 
		\hline
		DG 			& 24.66 & 10.58 & 15.02 & 14.78 & 10.03 & 10.34 & 8.52 & \textbf{7.58} \\
		\hline
		GF 		& 23.87 & 9.82 & 12.26 & 14.70 & 9.82 & 9.65 & 9.88 &\textbf{9.50} \\
		\hline
		WS 		& 26.30 & 13.46 & 17.60 & 17.92 & 13.42 & 13.15 & 12.81 &\textbf{12.51}\\
		\bottomrule
	\end{tabular}
	\caption{Average angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 14.80 & 8.74 & 10.29 & 11.36 & \textbf{7.69} & 8.27 & 8.37 & 7.83 \\ 
		\hline
		BS 			& 8.80 & 3.54 & 4.70 & 8.55 & \textbf{3.01} & 4.01 & 4.69 & 3.56 \\ 
		\hline
		DG 			& 15.42 & 7.53 & 10.68 & 11.85 & 6.74 & 7.47 & 6.17 &\textbf{5.18} \\
		\hline
		GF 		& 14.36 & 6.14 & 8.54 & 11.71 & 6.08 & \textbf{5.86} & 6.38 & 5.96\\
		\hline
		WS 		& 17.16 & 7.45 & 11.19 & 12.70 & 7.43 & 7.19 & 7.28 & \textbf{6.93} \\
		\bottomrule
	\end{tabular}
	\caption{Median angular error of the evaluation dataset. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l |l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 19.30\% & 24.75\% & 20.45\% & 15.86\% & \textbf{34.04\%} & 27.93\% & 26.46\% & 29.41\%\\ 
		\hline
		BS 			& 41.39\% & 62.28\% & 52.70\% & 24.30\% & \textbf{65.98\%} & 59.50\% &  52.56\% & 62.08\% \\ 
		\hline
		DG 			& 17.68\% & 31.05\% & 18.02\% & 13.64\% & 36.64\% & 30.20\% & 40.26\% &\textbf{49.04\%}\\
		\hline
		GF 		& 25.37\% & 43.56\% & 29.39\% & 13.78\% & 43.86\% & \textbf{44.85\%} & 40.42\% & 44.09\%\\
		\hline
		WS 		& 27.35\% & 37.25\% & 27.56\% & 14.42\% & 36.15\% & 38.55\% & 37.76\% & \textbf{39.15\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 40.82\% & 63.27\% & 54.23\% & 49.93\% &  66.76\% & 65.36\% & 65.12\% & \textbf{68.29\%} \\ 
		\hline
		BS 			& 54.04\% & 83.23\% & 79.37\% & 66.58\% & \textbf{83.62\%} & 82.43\% & 82.04\% & 83.15\%\\ 
		\hline
		DG 			& 40.87\% & 69.75\% & 52.93\% & 48.19\% & 72.64\% & 71.07\% & 77.83\% & \textbf{81.52\%}\\
		\hline
		GF 		& 43.67\% & 73.48\% & 63.11\% & 48.81\% & 73.28\% & 74.21\%  & 72.98\% &\textbf{74.48\%}\\
		\hline
		WS 		& 40.47\% & 62.63\% & 50.17\% & 44.74\% & 62.65\% & 63.73\% & 63.88\% & \textbf{65.07\%} \\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 11.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.}  & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 62.27\% & 90.02\% & 84.28\% & 83.93\% & 90.68\% & 90.59\% & 90.96\% & \textbf{92.04\%} \\ 
		\hline
		BS 			& 68.93\% & 93.26\% & 91.39\% & 88.58\% & 93.25\% & 93.22\% & 93.26\% & \textbf{93.47\%}\\ 
		\hline
		DG 			& 60.71\% & 90.11\% & 79.72\% & 82.45\% & 90.33\% & 90.99\% & 93.95\% & \textbf{94.78\%}\\
		\hline
		GF 		& 62.55\% & 89.83\% & 86.63\% & 83.47\% & 89.90\% & 90.18\% & 90.46\% &\textbf{90.72\%}\\
		\hline
		WS 		& 56.92\% & 81.03\% & 71.81\% & 73.11\% & 81.13\% & 81.72\% & 82.68\% &\textbf{83.37\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 22.5 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{tabular}{l | l | l l l | l l l l }
		\toprule
		\tabhead{Obj.} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		\midrule
		BL  		& 73.34\% & 95.92\% & 92.88\% & 93.20\% & 96.28\% & 96.06\% & 96.51\% &\textbf{96.85\%} \\ 
		\hline
		BS 			& 75.14\% & 95.80\% & 94.38\% & 93.22\% & 95.74\% & 95.76\% & 95.86\% &\textbf{96.00\% }\\ 
		\hline
		DG 			& 68.72\% & 94.69\% & 87.86\% & 90.61\% & 94.61\% & 95.10\% & 97.15\% & \textbf{97.61\%} \\
		\hline
		GF 		& 70.28\% & 93.76\% & 91.94\% & 90.96\% & 93.75\% & 94.04\% & 94.26\% & \textbf{94.29\%}\\
		\hline
		WS 		& 64.51\% & 87.48\% & 80.57\% & 82.72\% & 87.80\% & 87.90\% & 89.02\% & \textbf{89.30\%}\\
		\bottomrule
	\end{tabular}
	\caption{Percentage of error of less than 30 degrees of the evaluation data set. \textit{SVD} Neighborhood size $ k=2 $.}	
	\label{tab:eval-30d}
\end{table}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN_9.47.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison of GCNN based models. (Resolution: $ 128\times 128 $)}
	\label{fig:gcnn-eval-multi-model}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f3.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4_err_6.png}
		\caption{F4}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
	\label{fig:tripnet-fusion-eval}
\end{figure}
